```{r, echo=FALSE, include=FALSE}
# Don't set seed here. Set it in the .R file

serial <- paste0(sample(0:9, 4, TRUE), collapse = "")

n <- 50
x <- round(rnorm(n, mean = 15, sd = 3), 1)
gradientsign <- sample(c(-1, 1), 1)
gradient <- sample(1:5, 1)
intercept <- sample(1:10, 1)
y <- round(rnorm(n, mean = intercept + gradientsign * gradient,
                 sd = 2), 1)

mylm <- lm(y ~ x)

correctdigits <- 4
answer <- round2(unname(mylm$coefficients[2]), digits = correctdigits)

datadf <- data.frame(y = y, x = x)
write.csv(datadf, file = paste0("data", serial, ".csv"), row.names = FALSE)
```

Question
========
The `csv` file linked to below contains a random sample of `r n` observations of a dependent variable, $y$, and an independent variable, $x$.

Fit a linear regression model to the data and give the gradient of the regression line, correct to `r words(correctdigits)` decimal places.

[Download Data File](`r paste0("data", serial, ".csv")`)

*Note to marker: Question Version No. `r serial`.*


Solution
========
The correct answer is `r answer`. R code to find correct answer:

```
```{r, echo=FALSE, results='asis'}
cat("dat <- read.csv(\"", paste0("data", serial, ".csv"), "\") \n
mylm <- lm(y ~ x, data = dat) \n 
coef(mylm)[2]",
sep = "")
```
```

Meta-information
================
extype: num
exsolution: `r answer`
exname: `r paste0("calculate_gradient_", Sys.Date(), "_Rmd")`
extol: 0.0002
expoints: 3