```{r, echo=FALSE, include=FALSE}
# Don't set seed here. Set it in the .R file

serial <- paste0(sample(0:9, 4, TRUE), collapse = "")

n <- 50
x <- round(rnorm(n, mean = 15, sd = 3), 1)
gradientsign <- sample(c(-1, 1), 1)
gradient <- sample(1:5, 1)
intercept <- sample(1:10, 1)
y <- round(rnorm(n, mean = intercept + gradientsign * gradient,
                 sd = 2), 1)

datadf <- data.frame(y = y, x = x)
write.csv(datadf, file = paste0("data", serial, ".csv"), row.names = FALSE)
```

Question
========
The `csv` file linked to below contains a random sample of `r n` observations of a dependent variable, $y$, and an independent variable, $x$.

[Download Data File](`r paste0("data", serial, ".csv")`)

Create a scatter plot of the data. Save your plot as a JPEG image file and upload it along with the R code that you used to generate it.

*Note to marker: Question Version No. `r serial`.*


Solution
========

Plot should resemble the following:

```{r, echo=FALSE, fig.cap=""}
plot(x, y)
```

Or (using `ggplot2` package),

```{r, echo=FALSE, fig.cap=""}
df <- data.frame(x = x, y = y)
library(ggplot2)
ggplot(df, mapping = aes(x = x, y = y)) + 
  geom_point()
```


R code to find correct answer:

```
```{r, echo=FALSE, results='asis'}
cat("dat <- read.csv(\"", paste0("data", serial, ".csv"), "\") \n
plot(dat$x, dat$y, xlab = \"x\", ylab = \"y\") \n # OR: \n ggplot(dat, mapping = aes(x = x, y = y)) + \n geom_point()",
sep = "")
```
```

Marking scheme (where $\rule{1.5ex}{1.5ex}$ denotes one mark): $\rule{1.5ex}{1.5ex}$ for importing data; $\rule{1.5ex}{1.5ex}$ for plotting code; $\rule{1.5ex}{1.5ex}$ for correct scatter plot uploaded


Meta-information
================
extype: string
exstringtype: essay
exsolution: nil
exname: `r paste0("upload_scatterplot_essay_", Sys.Date(), "_Rmd")`
exextra[essay,logical]: TRUE
exextra[essay_format,character]: editor
exextra[essay_required,logical]: FALSE
exextra[essay_fieldlines,numeric]: 5
exextra[essay_attachments,numeric]: 1
exextra[essay_attachmentsrequired,logical]: TRUE
exmaxchars: 1000, 10, 50
expoints: 3